Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-15 paper/03_simulations.tex
fixed RD in vagueness_games.py; adapted batch script for values where non-convexity shows for low impairment

\section{Simulations}

@@

\subsection{Metrics}
\label{sec:metrics}
To be able to quantitively analyze the results of our simulations, we define a number of metrics to capture different characteristics of sim-max languages.

@@

\subsection{Methodology}
\newcommand{\impairment}{\alpha}
In our simulations we focus on a concrete setup in line with \cite{Correia2013:The-Bivalent-Tr}.
Namely, we define a similarity-maximization game with $\States = \Acts$, where $\States$ is a discrete set of equidistant points within the unit interval $[0,1]$, including the boundaries (thus we always use $n \geq 2$).
As similarity metric $s:\States \times \States \rightarrow [0,1]$, we use a negative exponential of the of the square distance, \emph{i.e.}~for $\state,\state^\prime \in \States$:
\begin{align*}
  s(\state,\state^\prime) =
    \begin{cases}
    1 & \textrm{if } \impairment = 0 \textrm{ and } \state = \state^\prime \\
    0 & \textrm{if } \impairment = 0 \textrm{ and } \state \neq \state^\prime \\
    e^{-\frac{\lVert \state - \state^\prime \rVert ^2}{\impairment^2}} & \textrm{otherwise} \\
    \end{cases}
\end{align*}
where $\impairment$ is an \emph{impairment} factor.
Here we deviate from \cite{Correia2013:The-Bivalent-Tr} by working with impairment $\impairment$ rather than acuity $\theta$, since we are interested in exploring the case of having $0$ impairment, and acuity does not have a natural maximum as defined.
Confusion is directly related with similarity, \emph{i.e.}~the more similar two states are, the more likely an agent is to perceive one as the other.
For simplicity, we equate one with the other by defining $C_{ij} = s(\state_i,\state_j)$.

@@

\subsection{Results}
In order to visualize the impact of the impairment factor on the outcome of simulations, we plot in Figure~\ref{fig:metrics-boxplots} the distribution of each of the measurements per impairment value.
%
\begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{plots/Speaker-entropy-20140813-194306}
                \caption{Entropy of sender strategy.}
%                \label{fig:gull}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{plots/Hearer-entropy-20140813-194306}
                \caption{Entropy of receiver strategy.}
        \end{subfigure}

>>>>

\section{Exploring the RDD}

\subsection{(Iterated) Diffusion}

We have seen that the \rdd can be conceptualized as a two-step
procedure. We first calculate where the replicator dynamic would take
us, and then apply diffusion. Since the latter step is the novel
addition, we should look at diffusion in isolation to understand what
the \rdd does.

\subsection{Simulations}

@@

\subsubsection{Metrics}
\label{sec:metrics}
To be able to quantitively analyze the results of our simulations, we define a number of metrics to capture different characteristics of sim-max languages.

@@

\subsubsection{Methodology}
\newcommand{\impairment}{\alpha}
In our simulations we focus on a concrete setup in line with \cite{Correia2013:The-Bivalent-Tr}.
Namely, we define a similarity-maximization game with $\States = \Acts$, where $\States$ is a discrete set of equidistant points within the unit interval $[0,1]$, including the boundaries (thus we always use $n \geq 2$).
As similarity metric $s:\States \times \States \rightarrow [0,1]$, we use a negative exponential of the of the square distance, \emph{i.e.}~for $\state,\state^\prime \in \States$:
\begin{align*}
  s(\state,\state^\prime) =
    \begin{cases}
    1 & \textrm{if } \impairment = 0 \textrm{ and } \state = \state^\prime \\
    0 & \textrm{if } \impairment = 0 \textrm{ and } \state \neq \state^\prime \\
    e^{-\frac{\lVert \state - \state^\prime \rVert ^2}{\impairment^2}} & \textrm{otherwise} \\
    \end{cases}
\end{align*}
where $\impairment$ is an \emph{impairment} factor.
Here we deviate from \cite{Correia2013:The-Bivalent-Tr} by working with impairment $\impairment$ rather than acuity $\theta$, since we are interested in exploring the case of having $0$ impairment, and acuity does not have a natural maximum as defined.
Confusion is directly related with similarity, \emph{i.e.}~the more similar two states are, the more likely an agent is to perceive one as the other.
For simplicity, we equate one with the other by defining $C_{ij} = s(\state_i,\state_j)$.

@@

\subsubsection{Results}
In order to visualize the impact of the impairment factor on the outcome of simulations, we plot in Figure~\ref{fig:metrics-boxplots} the distribution of each of the measurements per impairment value.
%
\begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{plots/Speaker-entropy-20140813-194306}
                \caption{Entropy of sender strategy.}
%                \label{fig:gull}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{plots/Hearer-entropy-20140813-194306}
                \caption{Entropy of receiver strategy.}
        \end{subfigure}

### 2014-09-15 snippets/data_exploration/data_exploration_tmp.Rmd
fixed RD in vagueness_games.py; adapted batch script for values where non-convexity shows for low impairment

require('ellipse')
require('ggplot2')
require('reshape2')
source('~//Desktop//data//svn//programming//R//helpers//helpers.R')

data = read.csv('results/20140813-194306.csv', 
                colClasses=c('numeric','factor','numeric','numeric','numeric',
                             'factor','numeric','numeric','numeric','numeric',
                             'numeric','numeric','numeric','numeric','numeric',
                             'numeric','character','character'))

>>>>

require('ellipse')
require('ggplot2')
require('reshape2')
source('~/Desktop/data/svn/programming/R/helpers/helpers.R')

data = read.csv('~/Desktop/data/svn/vagueness-games/results/20140915-190401.csv', 
                colClasses=c('numeric','factor','numeric','numeric','numeric',
                             'factor','numeric','numeric','numeric','numeric',
                             'numeric','numeric','numeric','numeric','numeric',
                             'numeric','character','character'))
